---
title: "Proteomics.analysis.data"
output: github_document
---

<!-- badges: start -->
[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

The `Proteomics.analysis.data` package was prepared by the 
MRC Toxicology unit [Bioinformatics](https://www.mrc-tox.cam.ac.uk/facilities/bioinformatics)
facility to provide data for training sessions covering the basics of proteomics analyses.

## Install

```{r, eval=FALSE}
remotes::install_github("MRCToxBioinformatics/Proteomics.analysis.data")
```

## Data
You can see the available data sets using the following
```{r, eval=FALSE}
list.files(system.file("extdata", package = "Proteomics.analysis.data"))
```

Note that the extdata is organised in subdirectories. Files will always have a suffix.
To see the files in the subdirectory, use, e.g
```{r, eval=FALSE}
list.files(system.file("extdata/OOPS_SILAC", package = "Proteomics.analysis.data"))
```

## Documentation
Data files documentation can be obtained via `help(package="Proteomics.analysis.data")`

